\documentclass[12pt, unicode]{beamer}
\usetheme{Warsaw}
\usepackage{luatexja}
\usepackage{color}
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily\bfseries,
  commentstyle=\color{red}\itshape,
  stringstyle=\color{black!30!green},
  showstringspaces=false,
  keywordstyle=\color{blue}\bfseries}
%color
\definecolor{battleshipgrey}{rgb}{0.52, 0.52, 0.51}

\title{Fluentd forward protocol modes in v0}
\subtitle{... and how to implement minimal Fluentd logger.}
\author{Hiroshi Hatake}
\date[2016/04/08]{Technical information sharing seminar}

\begin{document}

\frame{\maketitle}

\begin{frame}{Introduction}
\begin{block}{What is Fluentd?}
Fluentd is a fully free open-source log collector for unified logging layer.
\end{block}
\onslide<1->
\begin{itemize}
\item<2-> Unified logging with JSON and msgpack
\item<3-> Pluggable architecture
\item<4-> Minimum resources required
\item<5-> Built-in reliability
\end{itemize}
\end{frame}

\begin{frame}{Forward protocol - Introduction}
\begin{block}{Forward protocol\footnote[frame]{https://github.com/fluent/fluentd/wiki/Forward-Protocol-Specification-v0}}
Fluentd has three modes in forward protocol.
\end{block}
\begin{itemize}
\item<1-> Message Mode
\item<2-> Forward Mode
\item<3-> PackedForward Mode
\end{itemize}
\end{frame}

\begin{frame}{Message Mode protocol}
\begin{block}{Message Mode\footnote[frame]{https://github.com/fluent/fluentd/wiki/Forward-Protocol-Specification-v0\#message-mode}}
It carries just an event.
\end{block}
\begin{itemize}
\item \uncover<1->{\textbf {tag} is a string separated with '.' (e.g. myapp.access) to categorize events.}
\item \uncover<1->{\textbf {time} is a number of seconds since Unix epoch.}
\item \uncover<1->{\textbf {record} is key-value pairs of the event record.}
\item \uncover<2->{\color{battleshipgrey} \textbf {option} is optional key-value pairs, to bring data to control servers' behavior.}
\end{itemize}
\end{frame}

\begin{frame}{Message Mode protocol}
\begin{block}{Message Mode\footnote[frame]{https://github.com/fluent/fluentd/wiki/Forward-Protocol-Specification-v0\#message-mode}}
It carries just an event.
\end{block}
\begin{table}[htb]
\resizebox{\textwidth}{!}{%
    \begin{tabular}{l | c | c | c } \hline
      name & type & content & mandatory? \\ \hline \hline
      tag & str & tag name & yes \\ \hline
      time & Integer/EventTime(ext type) & Unix Time/Unix Time with nano seconds & yes \\ \hline
      record & Object(like HashMap) & pairs of keys(String) and values(Object) & yes \\ \hline
      option & Object(like HashMap) & pairs of keys(String) and values(Object) & no \\ \hline
    \end{tabular}}
\end{table}
\end{frame}

\begin{frame}{Forward Mode protocol}
\begin{block}{Forward Mode\footnote[frame]{https://github.com/fluent/fluentd/wiki/Forward-Protocol-Specification-v0\#forward-mode}}
It carries a series of events as a msgpack array on a single request.
\end{block}
\begin{itemize}
\item \uncover<1->{\textbf {tag} is a string separated with '.' (e.g. myapp.access) to categorize events.}
\item \uncover<1->{\textbf {entries}\footnote[frame]{https://github.com/fluent/fluentd/wiki/Forward-Protocol-Specification-v0\#entry} is an array of Entries which are pairs of Unix epoch and record.}
\item \uncover<2->{\color{battleshipgrey} \textbf {option} is optional key-value pairs, to bring data to control servers' behavior.}
\end{itemize}
\end{frame}

\begin{frame}{Forward Mode protocol}
\begin{block}{Forward Mode\footnote[frame]{https://github.com/fluent/fluentd/wiki/Forward-Protocol-Specification-v0\#forward-mode}}
It carries a series of events as a msgpack array on a single request.
\end{block}
\begin{table}[htb]
\resizebox{\textwidth}{!}{%
    \begin{tabular}{l | c | c | c } \hline
      name & type & content & mandatory? \\ \hline \hline
      tag & str & tag name & yes \\ \hline
      entries & Array & an array of Entries which are pairs of Unix epoch and record. & yes \\ \hline
      option & Object(like HashMap) & pairs of keys(String) and values(Object) & no \\ \hline
    \end{tabular}}
\end{table}
\end{frame}

\begin{frame}{PackedForward Mode protocol}
\begin{block}{PackedForward Mode\footnote[frame]{https://github.com/fluent/fluentd/wiki/Forward-Protocol-Specification-v0\#packedforward-mode}}
It carries a series of events as a msgpack binary on a single request.
\end{block}
\begin{itemize}
\item \uncover<1->{\textbf {tag} is a string separated with '.' (e.g. myapp.access) to categorize events.}
\item \uncover<1->{\textbf {entries} is a msgpack stream of Entry which contains pairs of Unix epoch and record msgpack binary.}
\item \uncover<2->{\color{battleshipgrey} \textbf {option} is optional key-value pairs, to bring data to control servers' behavior.}
\end{itemize}
\end{frame}

\begin{frame}{PackedForward Mode protocol}
\begin{block}{PackedForward Mode\footnote[frame]{https://github.com/fluent/fluentd/wiki/Forward-Protocol-Specification-v0\#packedforward-mode}}
It carries a series of events as a msgpack binary on a single request.
\end{block}
\begin{table}[htb]
\resizebox{\textwidth}{!}{%
    \begin{tabular}{l | c | c | c } \hline
      name & type & content & mandatory? \\ \hline \hline
      tag & str & tag name & yes \\ \hline
      entries & str | bin & a msgpack stream of Entry which contains pairs of Unix epoch and record. & yes \\ \hline
      option & Object(like HashMap) & pairs of keys(String) and values(Object) & no \\ \hline
    \end{tabular}}
\end{table}
\end{frame}

\begin{frame}{How to implement minimal Fluentd logger?}
\begin{block}{Minimal Fluentd logger implementation strategy}
\begin{itemize}
\item \uncover<1-> {{\textbf {Fluentd logger}} needs to send an event to Fluentd.}
  \begin{itemize}
  \item \uncover<2-> {{\textbf {Fluentd logger}} need {\textbf {not}} to add optional elements in sending events to Fluentd.}
  \item \uncover<3-> {{\textbf {Fluentd logger}} {\textbf {should}} use message mode to send events to Fluentd.}
  \end{itemize}
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{How to implement minimal Fluentd logger?}
\begin{block}{Minimal Fluentd logger implementation}
\begin{itemize}
\item \uncover<1-> {{\textbf {Fluentd logger}} needs to connect to Fluentd with TCP.}
\item \uncover<2-> {{\textbf {Fluentd logger}} send an event which contains tag, timespec, and record, to Fluentd.}
\item \uncover<3-> {{\textbf {Fluentd logger}} should disconnect connection against Fluentd immediately when sending an event.}
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{A short characteristics of Rust\footnote[frame]{https://www.rust-lang.org/}language}
\begin{block}{Characteristics}
Rust is a systems programming language that runs blazingly fast, prevents segfaults, and guarantees thread safety.
\end{block}
\begin{itemize}
\item \uncover<1-> {Guaranteed memory safety}
\item \uncover<2-> {Trait-based generics}
\item \uncover<3-> {Type inference etc.}
\end{itemize}
\end{frame}

\begin{frame}{About Rust language -- what is the weakness points of Rust language?}
\begin{block}{Weakness of Rust language}
Rust does not have...
\end{block}
\begin{itemize}
\item \uncover<1-> {Dynamic typing}
\item \uncover<2-> {Code simplicity}
\item \uncover<3-> {Easy to write code}
\end{itemize}
\end{frame}

% Set font size for annotation.
\newcommand\smallannotate{\fontsize{9}{9.2}\selectfont}
\begin{frame}{A short  exploration of Rust language}
\begin{block}{Fun things of Rust}
Rust makes you to benefit static type system because ... 
\end{block}
\begin{itemize}
\item \uncover<1-> {Flexible type by trait based generics}
\item \uncover<2-> {To clarify software specification}
\item \uncover<3-> {Well documented ecosystem etc. {\smallannotate(e.g. You don't create document when there is wrong code. Amazing!)}}
\end{itemize}
\end{frame}

%% Define highlighting for Rust.
\lstdefinelanguage{Rust} {
  morecomment = [l]{//},
  morecomment = [l]{///},
  morecomment = [s]{/*}{*/},
  morestring=[b]",
  sensitive = true,
  morekeywords = {extern, crate, fn, let, use, mut}
}
% Set font size for lstlisting.
\newcommand\Small{\fontsize{9}{9.2}\selectfont}
\begin{frame}[fragile]
fruently example:
\begin{lstlisting}[language={Rust},basicstyle=\ttfamily\Small]
extern crate fruently;
use fruently::fluent::Fluent;
use std::collections::HashMap;
use fruently::forwardable::JsonForwardable;

fn main() {
    // create record
    let mut obj: HashMap<String, String> = HashMap::new();
    obj.insert("name".to_string(), "fruently".to_string());
    // establish a TCP connection with Fluentd.
    let fruently = Fluent::new("0.0.0.0:24224", "test");
    // send json-encoded record to Fluentd
    // and disconnecting automatically.
    let _ = fruently.post(&obj);
}
\end{lstlisting}
\end{frame}

\frame{\centering \Large Demo}

\frame{\centering \Large Any questions?}

\end{document}
